\font\titlesize=cmbx10 scaled\magstep2
\font\namesize=cmbx10 scaled\magstep1
\vsize=10in
\hsize=8in
\voffset -0.4in
\hoffset -0.9in
\vskip 1cm
\centerline{\titlesize CURRICULUM VITAE}
\vskip 0.4in
\centerline{\namesize ALEX McGUIRE PhD}
\vskip 0.2in
\def\jobskip{\noalign{\bigskip}}
\def\posskip{\noalign{\medskip}}
\midinsert
\narrower\narrower\narrower
\noindent I am a senior quantitative analyst working for an energy trading company with extensive experience in building mathematical models for exotic options in 
different areas of finance, together with strong programming and systems development skills. Due to close contact with traders, and my own trading experience, I value
solutions for their practicality and usefulness, rather than any theoretical elegance. I enjoy teaching, and am comfortable with communicating my ideas to people with all
levels of experience, including those with very limited knowledge of financial maths.
\endinsert


\halign {\indent\bf#\hfil&\quad\vtop{\parindent=0pt\hsize=36em\hangindent.0em\strut#\strut}\cr
\jobskip
{\bf EMPLOYMENT}\cr
\jobskip
Oct 2001 -- Date&{\bf EDF Energy Merchants Ltd}\cr
&Mid City Place\cr
&71 High Holborn\cr
&London WCV 6ED\cr
\posskip
Position:&Senior Quantitative Analyst\cr
\posskip
Duties:&\quad Since joining EDF Energy Merchants, the main trading arm of the French power supplier, Electricit\'e de France, I have been responsible for developing
mathematical models for the company's entire portfolio of exotic deals, raging from asian options, fixed and floating strike spread options, to 
complex swing, storage and hydroelectric deals. Due to inherent differences with more established derivatives markets, such as fixed income or equity, this work
involves the creation of new models to describe the behaviour of prices, especially price spikes, as well as techniques to capture the effects of seasonality while 
keeping the number of model factors small.\cr
&\quad At EDF I have been greatly involved in the design and development of a risk management and pricing system, written using java, ruby, lisp and C. This
currently holds the deals for all the company's option books, around 200K deals. I have worked on this system since inception, writing
all but the very simplest models, tools to extrapolate finely grained prices and volatilities from imperfect market data, VAR reporting and many deal 
specific risk analysis reports.
Besides being solely responsible for the mathematical side of this system, I designed and implemented large parts of its infrastructure, 
including the schema for representing data, as well as the underlying database, and have also built a profiler, 
which has been fundamental in the construction of very fast models. \cr
&\quad This role requires me to work closely with people having different levels of knowledge of derivatives theory, including the heads and senior traders of the derivatives 
and structuring departments; quants and quant developers throughout the EDF group, to whom I present papers at seminars held at EDF's research centre at Paris; 
non-mathematical colleagues, with whom I enjoy the challenge of explaining my work in a non-technical way, so that they can develop an intuitive idea for the maths, as well
as the reasoning behind it.\cr
\jobskip
Apr 2000 -- Sep 2001 &{\bf Sempra Energy Trading}\cr
&Tower 42\cr
&25 Old Broad Street\cr
&London EC2N 1HQ\cr
\posskip
Position: &Senior Quantitative Analyst\cr
\posskip
Duties:&\quad This role involved the design of new models for Sempra's growing exotics business, working closely
with the structuring department in order that their deals closely matched their clients' risk requirements, while
minimising the exposure to unhedgeable risks. I maintained frequent contact with the head of derivatives and the principal traders, ensuring
that my models captured the most important risk factors relevant to each deal, and that the reporting tools were sufficient 
for their needs, making modifications for specific deal types where necessary.\cr
&\quad Along with a small team of developers, I was responsible for the design and development of a new trading/risk management system, which to the best of my knowledge 
is still the company's main source of risk reporting. I left Sempra to follow the head of derivatives to EDF.\cr
\jobskip
Sep 1999 -- March 2000 &{\bf Tokai Bank Europe}\cr
&1 Exchange Square\cr
&London EC2A 2JL\cr
\posskip
Position: &Contractor\cr
\posskip
Duties:&\quad This was a temporary role which involved the analysis of exotic option models being used in a system written in C++. I rewrote most of these models
in order to increase the number of complex deal types that could be handled, while avoiding the problems inherent with the Hull-White approach that had been taken
previously.\cr
\jobskip
Apr 1997 -- Aug 1999&{\bf IBJ International}\cr
&Bracken House\cr
&1 Friday Street\cr
&London EC4M 9JA\cr
\posskip
Position: &Exotic options trader / Quant developer\cr
\posskip
Duties:&\quad At IBJ I made markets in exotic interest rate and FX options, as well as dynamically hedging the portfolio. A large part of my time was spent working on an 
existing exotic options system, written in C++. Here I rewrote most of the models, giving them a more rigorous basis and generalising to a multi-factor setting. These models 
were significantly faster than those offered by commercial systems at the time. I greatly improved the system's generation of risk and hedging reports, turning a lengthy 
overnight process into one that took only minutes to complete, allowing much 
quicker responses to the sharp moves in interest and fx rates which then prevailed.\cr
&\quad The exotic options department was eventually closed due to the restructuring of the Japanese banking system at that time.\cr
\jobskip
Feb 1997 -- Mar 1997&{\bf Exco Money Broking UK Ltd}\cr
&119 Cannon Street\cr
&London EC4\cr
\posskip
Position: &Contractor\cr
\posskip
Duties:&This was a short temporary position for the development of tools to aid the brokers in their work, which was mostly in standard fixed income products, 
writing Excel spreadsheets linked with C++ DLLs. Besides fulfilling the usual requirements for such a company, such as the calculation of yield curves and swap pricing, 
I designed and implemented a real time 'shortest path' algorithm which found arbitrages for the basis swap brokers.\cr
\jobskip
Feb 1995 -- Dec 1996&{\bf Sumitomo Finance International}\cr
&Temple Court\cr
&11 Queen Victoria Street\cr
&London EC4N 4UQ\cr
\posskip
Position: &Options trader / Quant developer\cr
\posskip
Duties:&\quad Originally hired as a junior trader to assist in the market making and hedging of a JGB options book, my increasing interest in finance theory 
led to my running small, yet relatively profitable books which took advantage of various 
inefficiencies in the Japanese and German bond option markets. These inefficiencies included mispriced volatility smiles, incorrect volatility/duration curves and breakdowns 
in the relationships between bond options, repo and futures markets.
While at Sumitomo I developed all of the systems involved in the pricing, analysis and risk management of these options books, and wrote systems to help the other
fixed income traders in their work.\cr
&\quad I left Sumitomo due to the closure of the entire fixed income department, caused by the restructuring of the Japanese banking system at that time.\cr
\jobskip
April 1993 -- Feb 1995&{\bf Rolfe \& Nolan Plc}\cr
\posskip
Position: &Developer\cr
\posskip
Duties:&\quad Rolfe \& Nolan was a financial software house, developing systems for the management of positions in exchange traded futures and options. I worked in a 
mixture of C++ and VAX Basic, writing mostly valuation tools. My role required me to frequently meet with clients throughout the UK and Europe.\cr
\jobskip
Jan 1992 -- Apr 1993&{\bf Cumulus Systems Ltd}\cr
&1 High Street, Rickmansworth\cr
\posskip
Position: &Developer\cr
\posskip
Duties: &\quad I worked at Cumulus on a back office system for bond trading, writing various reporting tools and client screens.\cr
\noalign{\bigskip}
\noalign{\bigskip}
{\bf FURTHER EDUCATION}\cr
\noalign{\smallskip}
1988--1992&University of Exeter\cr
&PhD Commutative Algebra --- ``On the structure of partially ordered abelian groups with ICC, and integrally closed linearly compact domains''\cr
\noalign{\smallskip}
1984--1988&University of Sheffield\cr
&BSc (Hons) Mathematics I\cr
\noalign{\bigskip\bigskip}
{\bf OTHER QUALIFICATIONS}\cr
\noalign{\smallskip}
Mar 1995&SFA Securities and Financial Derivatives Representative\cr
Mar 1995&APT Trader Qualified\cr
\noalign{\bigskip\bigskip}
{\bf LANGUAGES}&French (functional)\cr
\noalign{\bigskip\bigskip}
{\bf LEISURE INTERESTS}&Computing theory; cooking; music.\cr
\noalign{\bigskip\bigskip}
{\bf ADDRESS}&19 Woodville Road\cr
&NP20 4JB\cr
&Newport\cr
&South Wales\cr
\noalign{\bigskip}
{\bf PHONE}&01633 246830 (Home)\cr
&07939 347222 (mobile)\cr
\noalign{\bigskip}
{\bf DATE OF BIRTH}&9 November 1966\cr
\noalign{\bigskip}
}

\bye